---
title: "Read new simulation results data"
output: html_document
date: "2025-04-03"
---

### Read datafile
```{r}
library(tidyverse)
library(papaja)
library(viridis)

# Change path depending on your path to combined_results_contaminants and all_cse_results
combined_results = read_csv("results/0505/combined_results_contaminants.csv")
cse_descriptives = read_csv("results/0505/all_cse_results.csv")

combined_results = combined_results %>% 
  left_join(., cse_descriptives, by=c("effect_size", "job_id", "participants", "filter_type", "df_id"))


cb_palette <- c(
  "#332288", # dark blue
  "#88CCEE", # light blue
  "#117733", # green
  "#DDCC27", # sand
  "#CC6677", # red
  "#AA4499", # purple
  "#44AA99",  # turquoise
  "#B62355", # dark magenta
  "#999933", # olive
  "#661100" # dark brown
)
```

```{r}
combined_results = combined_results %>% 
  mutate(evidence_for_cse = ifelse(model_id == 'anova', ifelse(p.value<.05 & cse>0, 1, 0), ifelse(evidence,1,0)),
         evidence_with_sesoi = ifelse(model_id == 'anova', ifelse(p.value<.05 & cse>0, 1, 0), ifelse(evidence==T & estimate< -1, 1,0))
         )
```



```{r}
large_effects = combined_results %>% 
  filter(effect_size == "large_effect")

small_effects = combined_results %>% 
  filter(effect_size == "small_effect")

large_no_effects = combined_results %>% 
  filter(effect_size == "large_no_effect")

small_no_effects = combined_results %>% 
  filter(effect_size == "small_no_effect")
```

#### Evidence test
```{r}
lmer_evidence_table = large_no_effects %>% #combined_results %>%
  filter(model_id != "anova") %>% 
  mutate(criteria_discrepancy = ifelse(p.value<.05 & evidence == FALSE & estimate<0, 1, 0))

lmer_evidence_table %>% count(criteria_discrepancy)


discrepancies = lmer_evidence_table %>% 
  filter(criteria_discrepancy == 1)
  
```



# Large effect read
```{r}
convergence_large = large_effects %>% 
  group_by(model_id) %>% 
  summarize(converged = mean(ifelse(convergence_status == "Converged", 1, 0))) %>% 
  filter(converged>0) %>% 
  pivot_wider(names_from = model_id, values_from = converged) %>% 
  mutate(dataset = "prime_probe")

convergence_small = small_effects %>% 
 group_by(model_id) %>% 
  summarize(converged = mean(ifelse(convergence_status == "Converged", 1, 0))) %>% 
  filter(converged>0) %>% 
  pivot_wider(names_from = model_id, values_from = converged) %>% 
  mutate(dataset = "flanker")

convergence_small_no = small_no_effects %>% 
 group_by(model_id) %>% 
  summarize(converged = mean(ifelse(convergence_status == "Converged", 1, 0))) %>% 
  filter(converged>0) %>% 
  pivot_wider(names_from = model_id, values_from = converged) %>% 
  mutate(dataset = "prime_probe_no_effect")

convergence_large_no = large_no_effects %>% 
  group_by(model_id) %>% 
  summarize(converged = mean(ifelse(convergence_status == "Converged", 1, 0))) %>% 
  filter(converged>0) %>% 
  pivot_wider(names_from = model_id, values_from = converged) %>% 
  mutate(dataset = "flanker_no_effect")

convergence_table = rbind(convergence_large, convergence_small, convergence_large_no, convergence_small_no)


flextable::flextable(convergence_table)

```

### Visual jitter for ggplots
```{r}
offsets_participants <- c('anova' = -1, 'simple_lmer' = 1, 'full_lmer' = -1, 'simple_log_lmer' = 1,'full_log_lmer' = -1)
offsets_tprs <- c('anova' = -.002, 'simple_lmer' = .002, 'full_lmer' = -.002, 'simple_log_lmer' = .002,'full_log_lmer' = -.002)
offsets_participants
```

```{r}

large_summary_table_models = large_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id, participants) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            ) %>% 
   mutate(participant_jitter = participants + offsets_participants[model_id],
          TPR_jitter = TPR + offsets_tprs[model_id])
  
```
```{r}
large_summary_model_results = large_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            ) 
large_summary_model_results
```

```{r}
large_summary_plot_models = large_summary_table_models %>% 
  ggplot() +
  aes(x=participant_jitter, y=TPR_jitter, group = model_id, color = model_id)+
  geom_point()+
  geom_path() +
  scale_color_manual(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"),
                       values= cb_palette)+
  scale_x_continuous(name = "Participants", breaks = c(25, 50, 100, 200, 400))+
  scale_y_continuous(name = "TPR",limits = c(0,1.05), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

large_summary_plot_models
ggsave("all_models.png", dpi = 600, width = 8, height = 4)
```

#### NOEFFECT

```{r}
large_no_effects = combined_results %>% 
  filter(effect_size == "large_no_effect")

no_large_summary_table_models = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id, participants) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            ) %>% 
   mutate(participant_jitter = participants + offsets_participants[model_id],
          FPR_jitter = FPR + offsets_tprs[model_id])

```


```{r}
no_large_summary_results = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova",
         filter_type == "mad_2.0") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
no_large_summary_results
```

```{r}
no_large_summary_sesoi = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova",
         filter_type == "mad_2.0") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            FPR = mean(evidence_with_sesoi, na.rm = T),
            evidence_sd = sd(evidence_with_sesoi, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
no_large_summary_sesoi
```

```{r}
no_large_summary_plot_models = no_large_summary_table_models %>% 
  ggplot() +
  aes(x=participant_jitter, y=FPR_jitter, group = model_id, color = model_id)+
  geom_point()+
  geom_path() +
  scale_color_manual(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"),
                       values= cb_palette)+
  scale_x_continuous(name="Participants", breaks = c(25, 50, 100, 200, 400))+
  scale_y_continuous(name = "FPR",limits = c(0,1.05), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

no_large_summary_plot_models
ggsave("no_all_models.png", dpi = 600, width = 8, height = 4)
```

### Combined plot

```{r}
combined_roc_plot_large = no_large_summary_table_models %>% 
  select(FPR,FPR_jitter, model_id, participants) %>% 
  left_join(., large_summary_table_models, by=c("participants", "model_id")) %>% 
  mutate(participants = factor(participants, levels = c(25, 50, 100, 200, 400), ordered = TRUE),
         participant_jitter = offsets_participants[model_id])

combined_roc_plot_large = combined_roc_plot_large[order(combined_roc_plot_large$model_id, combined_roc_plot_large$participants), ]


combined_roc_plot_large %>% ggplot(aes(x = FPR, y = TPR, group = model_id, color = model_id)) +
  geom_vline(xintercept = 0.025, linetype = "dashed", color = "grey", alpha=.6)+
  geom_path() +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = participants), size = 2.5, max.overlaps = 10, show.legend = FALSE, segment.color=NA) +
  scale_color_manual(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"),
                       values= cb_palette)+
  labs(x = "False Positive Rate (FPR)",
       y = "True Positive Rate (TPR)",
       color = "Model") +
  scale_x_continuous(limits = c(0,.2),breaks = c(0, .025, .05, .1, .15, .2))+
  scale_y_continuous(limits = c(0,1), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

ggsave("ROC_all_models.png", dpi = 600, width = 8, height = 4)
```

## NO FILTER MODELS
```{r}
large_summary_table_models_nofilter = large_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova",
         filter_type == "no_filter") %>% 
  group_by(model_id, participants) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            ) %>% 
   mutate(participant_jitter = participants + offsets_participants[model_id],
          TPR_jitter = TPR + offsets_tprs[model_id])
```
```{r}
large_summary_models_nofilter_results = large_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova",
         filter_type == "no_filter") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )
large_summary_models_nofilter_results
```

```{r}
large_summary_plot_models_nofilter = large_summary_table_models_nofilter %>% 
  ggplot() +
  aes(x=participant_jitter, y=TPR_jitter, group = model_id, color = model_id)+
  geom_point()+
  geom_path() +
  scale_color_manual(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"),
                       values= cb_palette)+
  scale_x_continuous(name = "Participants", breaks = c(25, 50, 100, 200, 400))+
  scale_y_continuous(name = "TPR",limits = c(0,1.05), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

large_summary_plot_models_nofilter
ggsave("all_models_nofilter.png", dpi = 600, width = 8, height = 4)
```

#### NOEFFECT

```{r}

no_large_summary_table_models_nofilter = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova",
         filter_type == "no_filter") %>% 
  group_by(model_id, participants) %>% 
   summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            ) %>% 
   mutate(participant_jitter = participants + offsets_participants[model_id],
          FPR_jitter = FPR + offsets_tprs[model_id])

no_large_summary_results_nofilter = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova",
         filter_type == "no_filter") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
no_large_summary_results_nofilter
```


```{r}
no_large_summary_plot_models_nofilter = no_large_summary_table_models_nofilter %>% 
  ggplot() +
  aes(x=participant_jitter, y=FPR_jitter, group = model_id, color = model_id)+
  geom_point()+
  geom_path() +
  scale_color_manual(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"),
                       values= cb_palette)+
  scale_x_continuous(name="Participants", breaks = c(25, 50, 100, 200, 400))+
  scale_y_continuous(name = "FPR",limits = c(0,1.05), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

no_large_summary_plot_models_nofilter
ggsave("no_all_models_nofilter.png", dpi = 600, width = 8, height = 4)
```

### Nofilter ROC
```{r}
combined_roc_plot_large_nofilter = no_large_summary_table_models_nofilter %>% 
  select(FPR,FPR_jitter, model_id, participants) %>% 
  left_join(., large_summary_table_models_nofilter, by=c("participants", "model_id")) %>% 
  mutate(participants = factor(participants, levels = c(25, 50, 100, 200, 400), ordered = TRUE),
         participant_jitter = offsets_participants[model_id])

combined_roc_plot_large_nofilter = combined_roc_plot_large_nofilter[order(combined_roc_plot_large_nofilter$model_id, combined_roc_plot_large_nofilter$participants), ]


combined_roc_plot_large_nofilter %>% ggplot(aes(x = FPR, y = TPR, group = model_id, color = model_id)) +
  geom_vline(xintercept = 0.025, linetype = "dashed", color = "grey", alpha=.6)+
  geom_path() +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = participants), size = 2.5, max.overlaps = 10, show.legend = FALSE, segment.color = NA, min.segment.length = 0.2) +
  scale_color_manual(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"),
                       values= cb_palette)+
  labs(x = "False Positive Rate (FPR)",
       y = "True Positive Rate (TPR)",
       color = "Model") +
  scale_x_continuous(limits = c(0,.2),breaks = c(0, .025, .05, .1, .15, .2))+
  scale_y_continuous(limits = c(0,1), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

ggsave("ROC_nofilter_large.png", dpi = 600, width = 8, height = 4)
```

### 3.0SD FILTER MODELS
```{r}
large_summary_table_models_3 = large_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova",
         filter_type == "sd_3.0") %>% 
  group_by(model_id, participants) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )
```
```{r}
large_summary_models_3_results = large_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova",
         filter_type == "sd_3.0") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )
large_summary_models_3_results
```

```{r}
large_summary_plot_models_3 = large_summary_table_models_3 %>% 
  ggplot() +
  aes(x=participants, y=TPR, group = model_id, color = model_id)+
  geom_point()+
  geom_path(alpha = .6) +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()

large_summary_plot_models_3
ggsave("all_models_3.png", dpi = 600, width = 8, height = 4)
```

#### NOEFFECT

```{r}

no_large_summary_table_models_3 = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova",
         filter_type == "sd_3.0") %>% 
  group_by(model_id, participants) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )

no_large_summary_results_3 = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova",
         filter_type == "sd_3.0") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
no_large_summary_results_3
```


```{r}
no_large_summary_plot_models_3 = no_large_summary_table_models_3 %>% 
  ggplot() +
  aes(x=participants, y=FPR, group = model_id, color = model_id)+
  geom_point()+
  geom_path() +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()

no_large_summary_plot_models_3
ggsave("no_all_models_3.png", dpi = 600, width = 8, height = 4)
```

### 3SD ROC
```{r}
combined_roc_plot_large_3 = no_large_summary_table_models_3 %>% 
  select(FPR, model_id, participants) %>% 
  left_join(., large_summary_table_models_3, by=c("participants", "model_id")) %>% 
  mutate(participants = factor(participants, levels = c(25, 50, 100, 200, 400), ordered = TRUE),
         participant_jitter = offsets_participants[model_id])

combined_roc_plot_large_3 = combined_roc_plot_large_3[order(combined_roc_plot_large_3$model_id, combined_roc_plot_large_3$participants), ]


combined_roc_plot_large_3 %>% ggplot(aes(x = FPR, y = TPR, group = model_id, color = model_id)) +
  geom_vline(xintercept = 0.025, linetype = "dashed", color = "grey", alpha=.6)+
  geom_path() +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = participants), size = 2.5, max.overlaps = 10, show.legend = FALSE, segment.color = NA, min.segment.length = 0.2) +
  scale_color_manual(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"),
                       values= cb_palette)+
  labs(x = "False Positive Rate (FPR)",
       y = "True Positive Rate (TPR)",
       color = "Model") +
  scale_x_continuous(limits = c(0,.2),breaks = c(0, .025, .05, .1, .15, .2))+
  scale_y_continuous(limits = c(0,1), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

ggsave("ROC_3SD_large.png", dpi = 600, width = 8, height = 4)
```

# OUTLIER FILTERS

```{r}
large_summary_table_filters = large_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(filter_type, participants) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )

```
```{r}
large_summary_table_filters_results = large_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(filter_type) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )
large_summary_table_filters_results
```

```{r}
large_summary_plot_filters = large_summary_table_filters %>% 
  ggplot() +
  aes(x=participants, y=TPR, group = filter_type, color = filter_type)+
  geom_point()+
  geom_path() +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()
large_summary_plot_filters
ggsave("all_filters.png", dpi = 600, width = 8, height = 4)
```

### NO EFFECT
```{r}
no_large_summary_table_filters = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(filter_type, participants) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )

```
```{r}
no_large_summary_table_filters_results = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(filter_type) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
no_large_summary_table_filters_results
```
### Large Filters ROC
```{r}
combined_roc_plot_filters = no_large_summary_table_filters %>% 
  select(FPR, filter_type, participants) %>% 
  left_join(., large_summary_table_filters, by=c("participants", "filter_type")) %>% 
  mutate(participants = factor(participants, levels = c(25, 50, 100, 200, 400), ordered = TRUE),
         participant_jitter = offsets_participants[filter_type])

combined_roc_plot_filters = combined_roc_plot_filters[order(combined_roc_plot_filters$filter_type, combined_roc_plot_filters$participants), ]


combined_roc_plot_filters %>% ggplot(aes(x = FPR, y = TPR, group = filter_type, color = filter_type)) +
  geom_vline(xintercept = 0.025, linetype = "dashed", color = "grey", alpha=.6)+
  geom_path() +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = participants), size = 2.5, max.overlaps = 10, show.legend = FALSE, segment.color = NA, min.segment.length = 0.2) +
  scale_color_manual(name = "Filter Type", 
                       labels = c("no_filter" = "No outlier filter",
                                  "mad_2.0" = "+-2 MAD",
                                  "mad_2.5" = "+-2.5 MAD",
                                  "mad_3.0" = "+-3 MAD",
                                  "sd_2.0" = "+-2 SD",
                                  "sd_2.5" = "+-2.5 SD",
                                  "sd_3.0" = "+-3 SD",
                                  "time_1" = "200 ms < RT < 1000 ms",
                                  "time_1.25" = "200 ms < RT < 1250 ms",
                                  "time_1.5" = "200 ms < RT < 1500 ms"
                                  ),
                       values=cb_palette)+
  labs(x = "False Positive Rate (FPR)",
       y = "True Positive Rate (TPR)",
       color = "Model") +
  scale_x_continuous(limits = c(0,.2),breaks = c(0, .025, .05, .1, .15, .2))+
  scale_y_continuous(limits = c(0,1), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

ggsave("ROC_filters_large.png", dpi = 600, width = 8, height = 4)
```


### All combinations
```{r}
large_summary_results = large_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id, filter_type) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )

large_summary_results
```
### All combinations no effect
```{r}
large_summary_no_results = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id, filter_type) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )

large_summary_no_results
```


```{r}
no_large_summary_table_results = large_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id,filter_type) %>% 
  summarize(N = n(),
            FPR = mean(ifelse(model_id == 'anova', ifelse(p.value<.05, 1, 0), ifelse(evidence,1,0)), na.rm = T),
            evidence_sd = sd(ifelse(model_id == 'anova', ifelse(p.value<.05, 1, 0), ifelse(evidence,1,0)), na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
no_large_summary_table_results
```


### small effect read

```{r}
small_summary_table_models = small_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id, participants) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )

small_summary_table_models_results = small_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )
small_summary_table_models_results
```
```{r}
small_summary_models_plot = small_summary_table_models %>% 
ggplot() +
  aes(x=participants, y=TPR, group = model_id, color = model_id)+
  geom_point()+
  geom_path(alpha = .6) +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()

small_summary_models_plot
ggsave(plot=small_summary_models_plot,"small_models.png", dpi = 600, width = 8, height = 4)
```

#### NO EFFECT
```{r}
small_no_summary_table_models = small_no_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id, participants) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )

small_no_summary_table_models_results = small_no_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
small_no_summary_table_models_results
```
```{r}
no_small_summary_models_plot = small_no_summary_table_models %>% 
ggplot() +
  aes(x=participants, y=FPR, group = model_id, color = model_id)+
  geom_point()+
  geom_path(alpha = .6) +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()

no_small_summary_models_plot
ggsave(plot=no_small_summary_models_plot,"no_small_models.png", dpi = 600, width = 8, height = 4)
```

### ROC SMALL aLL
```{r}
combined_roc_plot_small = small_no_summary_table_models %>% 
  select(FPR, model_id, participants) %>% 
  left_join(., small_summary_table_models, by=c("participants", "model_id")) %>% 
  mutate(participants = factor(participants, levels = c(25, 50, 100, 200, 400), ordered = TRUE),
         participant_jitter = offsets_participants[model_id])

combined_roc_plot_small = combined_roc_plot_small[order(combined_roc_plot_small$model_id, combined_roc_plot_small$participants), ]


combined_roc_plot_small %>% ggplot(aes(x = FPR, y = TPR, group = model_id, color = model_id)) +
  geom_vline(xintercept = 0.025, linetype = "dashed", color = "grey", alpha=.6)+
  geom_path() +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = participants), size = 2.5, max.overlaps = 10, show.legend = FALSE, segment.color = NA, min.segment.length = 0.2) +
  scale_color_manual(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"),
                       values= cb_palette)+
  labs(x = "False Positive Rate (FPR)",
       y = "True Positive Rate (TPR)",
       color = "Model") +
  scale_x_continuous(limits = c(0,.2),breaks = c(0, .025, .05, .1, .15, .2))+
  scale_y_continuous(limits = c(0,1), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

ggsave("ROC_all_small.png", dpi = 600, width = 8, height = 4)
```

## NOFILTER SMALL
```{r}
small_summary_table_models_nofilter = small_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  filter(filter_type == "no_filter") %>% 
  group_by(model_id, participants) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )

small_summary_table_models_results_nofilter = small_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  filter(filter_type == "no_filter") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )
small_summary_table_models_results_nofilter
```

```{r}
small_summary_models_plot_nofilter = small_summary_table_models_nofilter %>% 
ggplot() +
  aes(x=participants, y=TPR, group = model_id, color = model_id)+
  geom_point()+
  geom_path(alpha = .6) +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()

small_summary_models_plot_nofilter
ggsave(plot=small_summary_models_plot_nofilter,"small_models_nofilter.png", dpi = 600, width = 8, height = 4)

```

#### NO EFFECT
```{r}
no_small_summary_table_models_nofilter = small_no_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  filter(filter_type == "no_filter") %>% 
  group_by(model_id, participants) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )

no_small_summary_table_models_results_nofilter = small_no_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  filter(filter_type == "no_filter") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
no_small_summary_table_models_results_nofilter
```

```{r}
no_small_summary_models_plot_nofilter = no_small_summary_table_models_nofilter %>% 
ggplot() +
  aes(x=participants, y=FPR, group = model_id, color = model_id)+
  geom_point()+
  geom_path(alpha = .6) +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()

no_small_summary_models_plot_nofilter
ggsave(plot=no_small_summary_models_plot_nofilter,"no_small_models_nofilter.png", dpi = 600, width = 8, height = 4)

```

### ROC SMALL NOFILTER
```{r}
combined_roc_plot_small_nofilter = no_small_summary_table_models_nofilter %>% 
  select(FPR, model_id, participants) %>% 
  left_join(., small_summary_table_models_nofilter, by=c("participants", "model_id")) %>% 
  mutate(participants = factor(participants, levels = c(25, 50, 100, 200, 400), ordered = TRUE),
         participant_jitter = offsets_participants[model_id])

combined_roc_plot_small_nofilter = combined_roc_plot_small_nofilter[order(combined_roc_plot_small_nofilter$model_id, combined_roc_plot_small_nofilter$participants), ]


combined_roc_plot_small_nofilter %>% ggplot(aes(x = FPR, y = TPR, group = model_id, color = model_id)) +
  geom_vline(xintercept = 0.025, linetype = "dashed", color = "grey", alpha=.6)+
  geom_path() +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = participants), size = 2.5, max.overlaps = 10, show.legend = FALSE, segment.color = NA, min.segment.length = 0.2) +
  scale_color_manual(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"),
                       values= cb_palette)+
  labs(x = "False Positive Rate (FPR)",
       y = "True Positive Rate (TPR)",
       color = "Model") +
  scale_x_continuous(limits = c(0,.2),breaks = c(0, .025, .05, .1, .15,.2))+
  scale_y_continuous(limits = c(0,1), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

ggsave("ROC_nofilter_small.png", dpi = 600, width = 8, height = 4)
```


## 3.0SD SMALL
```{r}
small_summary_table_models_3 = small_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  filter(filter_type == "sd_3.0") %>% 
  group_by(model_id, participants) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )

small_summary_table_models_results_3 = small_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  filter(filter_type == "sd_3.0") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )
small_summary_table_models_results_3
```

```{r}
small_summary_models_plot_3 = small_summary_table_models_3 %>% 
ggplot() +
  aes(x=participants, y=TPR, group = model_id, color = model_id)+
  geom_point()+
  geom_path(alpha = .6) +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()

small_summary_models_plot_3
ggsave(plot=small_summary_models_plot_3,"small_models_3.png", dpi = 600, width = 8, height = 4)

```

#### NO EFFECT
```{r}
no_small_summary_table_models_3 = small_no_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  filter(filter_type == "sd_3.0") %>% 
  group_by(model_id, participants) %>% 
   summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )

no_small_summary_table_models_results_3 = small_no_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  filter(filter_type == "sd_3.0") %>% 
  group_by(model_id) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
no_small_summary_table_models_results_3
```

```{r}
no_small_summary_models_plot_3 = no_small_summary_table_models_3 %>% 
ggplot() +
  aes(x=participants, y=FPR, group = model_id, color = model_id)+
  geom_point()+
  geom_path(alpha = .6) +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()

no_small_summary_models_plot_3
ggsave(plot=no_small_summary_models_plot_3,"no_small_models_3.png", dpi = 600, width = 8, height = 4)

```

### ROC SMALL 3SD
```{r}
combined_roc_plot_small_3SD = no_small_summary_table_models_3 %>% 
  select(FPR, model_id, participants) %>% 
  left_join(., small_summary_table_models_3, by=c("participants", "model_id")) %>% 
  mutate(participants = factor(participants, levels = c(25, 50, 100, 200, 400), ordered = TRUE),
         participant_jitter = offsets_participants[model_id])

combined_roc_plot_small_3SD = combined_roc_plot_small_3SD[order(combined_roc_plot_small_3SD$model_id, combined_roc_plot_small_3SD$participants), ]


combined_roc_plot_small_3SD %>% ggplot(aes(x = FPR, y = TPR, group = model_id, color = model_id)) +
  geom_vline(xintercept = 0.025, linetype = "dashed", color = "grey", alpha=.6)+
  geom_path() +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = participants), size = 2.5, max.overlaps = 10, show.legend = FALSE, segment.color = NA, min.segment.length = 0.2) +
  scale_color_manual(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"),
                       values= cb_palette)+
  labs(y = "False Positive Rate (FPR)",
       x = "True Positive Rate (TPR)",
       color = "Model") +
  scale_x_continuous(limits = c(0,.2),breaks = c(0, .025, .05, .1, .15,.2))+
  scale_y_continuous(limits = c(0,1), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()
ggsave("ROC_3SD_small.png", dpi = 600, width = 8, height = 4)
```


```{r}
#### OUTLIER FILTERS

small_summary_table_filters = small_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(filter_type, participants) %>% 
 summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )

```

```{r}
small_summary_table_filters_results = small_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(filter_type) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )
small_summary_table_filters_results
```

```{r}
small_summary_plot_filters = small_summary_table_filters %>% 
  ggplot() +
  aes(x=participants, y=TPR, group = filter_type, color = filter_type)+
  geom_point()+
  geom_path() +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()
small_summary_plot_filters
ggsave(plot = small_summary_plot_filters, "small_filters.png", dpi = 600, width = 8, height = 4)
```

### NO EFFECT
```{r}
no_small_summary_table_filters = small_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(filter_type, participants) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )

```
```{r}
no_small_summary_table_filters_results = small_no_effects %>% 
  filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(filter_type) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
no_small_summary_table_filters_results
```
```{r}
no_small_summary_plot_filters = no_small_summary_table_filters %>% 
  ggplot() +
  aes(x=participants, y=FPR, group = filter_type, color = filter_type)+
  geom_point()+
  geom_path() +
  ylim(0,1)+
  scale_color_discrete(name = "Model Type", 
                       labels = c("anova" = "ANOVA",
                                  "full_lmer" = "complex LMM",
                                  "simple_lmer" = "simple LMM",
                                  "simple_log_lmer" = "simple LMM with log(RT)",
                                  "full_log_lmer" = "complex LMM with log(RT)"))+
  scale_x_continuous(breaks = c(25, 50, 100, 200, 400))+
  papaja::theme_apa()
no_small_summary_plot_filters
ggsave(plot = no_small_summary_plot_filters, "no_small_filters.png", dpi = 600, width = 8, height = 4)
```
### ROC SMALL Conditions
```{r}
combined_roc_plot_small_filters = no_small_summary_table_filters %>% 
  select(FPR, filter_type, participants) %>% 
  left_join(., small_summary_table_filters, by=c("participants", "filter_type")) %>% 
  mutate(participants = factor(participants, levels = c(25, 50, 100, 200, 400), ordered = TRUE),
         participant_jitter = offsets_participants[filter_type])

combined_roc_plot_small_filters = combined_roc_plot_small_filters[order(combined_roc_plot_small_filters$filter_type, combined_roc_plot_small_filters$participants), ]


combined_roc_plot_small_filters %>% ggplot(aes(x = FPR, y = TPR, group = filter_type, color = filter_type)) +
  geom_vline(xintercept = 0.025, linetype = "dashed", color = "grey", alpha=.6)+
  geom_path() +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = participants), size = 2.5, max.overlaps = 10, show.legend = FALSE, segment.color = NA, min.segment.length = 0.2) +
  scale_color_manual(name = "Filter Type", 
                       labels = c("no_filter" = "No outlier filter",
                                  "mad_2.0" = "+-2 MAD",
                                  "mad_2.5" = "+-2.5 MAD",
                                  "mad_3.0" = "+-3 MAD",
                                  "sd_2.0" = "+-2 SD",
                                  "sd_2.5" = "+-2.5 SD",
                                  "sd_3.0" = "+-3 SD",
                                  "time_1" = "200 ms < RT < 1000 ms",
                                  "time_1.25" = "200 ms < RT < 1250 ms",
                                  "time_1.5" = "200 ms < RT < 1500 ms"
                                  ),
                       values=cb_palette)+
  labs(x = "False Positive Rate (FPR)",
       y = "True Positive Rate (TPR)",
       color = "Model") +
  scale_x_continuous(limits = c(0,.2),breaks = c(0, .025, .05, .1, .15,.2))+
  scale_y_continuous(limits = c(0,1), breaks = c(0, .2, .4, .6, .8, 1))+
  papaja::theme_apa()

ggsave("ROC_filters_small.png", dpi = 600, width = 8, height = 4)
```


### all combinations small
```{r}
small_summary_table_results = small_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id,filter_type) %>% 
  summarize(N = n(),
            TPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = TPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = TPR+1.96*(evidence_sd/sqrt(N))
            )
small_summary_table_results
```
no effect
```{r}
small_no_summary_table_results = small_no_effects %>% 
   filter(convergence_status == "Converged" | model_id == "anova") %>% 
  group_by(model_id,filter_type) %>% 
  summarize(N = n(),
            FPR = mean(evidence_for_cse, na.rm = T),
            evidence_sd = sd(evidence_for_cse, na.rm = T),
            lower_ci = FPR-1.96*(evidence_sd/sqrt(N)),
            upper_ci = FPR+1.96*(evidence_sd/sqrt(N))
            )
small_no_summary_table_results
```
